Synthesizing Symmetric Lenses

### 2019-02-28 papers/SymmetricLenses/main.tex
respond to comments and update intro and abstract

We describe an implementation of simple symmetric lenses and our synthesis
procedure as extensions to the Boomerang language. We evaluate
its performance on 48 benchmark examples drawn from Flash Fill,
Augeus, the bidirectional programming literature, and electronic
file format synchronization tasks. Our implementation can synthesize all these
lenses in under 30 seconds.  \bcp{All of them together take 30 seconds?  Or
  the maximum time it takes for one is 30 seconds?}
\end{abstract}

@@

However, the set of real-world use cases for bijective lenses, where two
data formats contain different arrangements of precisely the same
information, is  
limited.  A more common situation is where two data
formats share just {\em some} of their information content.  For instance,
two related database tables might share four out of five columns, but each
might have a different fifth column.  Or one ad-hoc system-configuration
file might include some format-specific metadata, such as a date or a
reference number, while the same configuration file on another operating
system does not.  Indeed among the 48 benchmark problems described in
Section \ref{sec:evaluation} below, all of the benchmarks taken from Flash
Fill~\cite{flashfill} and many of the benchmarks that synchronize between
two ad hoc file formats have this characteristic, 13 benchmarks in
total.  \bcp{I don't understand this.  We say that the non-bijective
  situation is ``more common,'' but we support this by saying that 13 out of
48 benchmarks (that we chose!) are non-bijective.  Or am I misreading??}

>>>>

We describe an implementation of simple symmetric lenses and our synthesis
procedure as extensions to the Boomerang language. We evaluate its performance
on 48 benchmark examples drawn from Flash Fill, Augeus, the bidirectional
programming literature, and electronic file format synchronization tasks. Our
implementation can synthesize each of these lenses in under 30 seconds.
\end{abstract}

@@

However, the set of real-world use cases for bijective lenses, where two
data formats contain different arrangements of precisely the same
information, is  
limited.  Oftentimes, two data
formats share just {\em some} of their information content.  For instance,
two related database tables might share four out of five columns, but each
might have a different fifth column.  Or one ad-hoc system-configuration
file might include some format-specific metadata, such as a date or a
reference number, while the same configuration file on another operating
system does not.  Indeed among the 48 benchmark problems described in
Section \ref{sec:evaluation} below, all of the benchmarks taken from Flash
Fill~\cite{flashfill} and many of the benchmarks that synchronize between
two ad hoc file formats have this characteristic, 13 benchmarks in
total.  \bcp{I don't understand this.  We say that the non-bijective
  situation is ``more common,'' but we support this by saying that 13 out of
48 benchmarks (that we chose!) are non-bijective.  Or am I misreading??} \afm{I
think this is due, in part, to where we got the benchmarks (Augeas typically removes
little information). I do think that
it is more common, but I suppose I have no real data on that. I've updated
the wording to be ``safer''.}
